\begin{rubric}{Invited Talks}
    \entry*[2023] Special Lecture, Dongguk University, Multimedia Software Engineering
    \par \textbf{Can the Metaverse Become the Future?}, Sep. 8, 2023. \vspace{0.5em}
    %
    \entry*[2022] Special Lecture, Gwangju Information \& Culture Industry Promotion Agency (AICL)
    \par \textbf{Startup Stories from the Field}, Nov. 18, 2022. \vspace{0.5em}
    %
    \entry*[2022] Special Lecture, Dongguk University, Multimedia Software Engineering
    \par \textbf{Startup Stories from the Field}, Nov. 11, 2022. \vspace{0.5em}
    %
    \entry*[2021] Special Lecture, Dongguk University, Multimedia Software Engineering
    \par \textbf{Convergence Technologies and Startups}, Sep. 16, 2021. \vspace{0.5em}
    %
    \entry*[2021] Special Lecture, Korea Institute of Startup \& Entrepreneurship Development
    \par \textbf{Convergence Technologies and Case Studies}, Apr. 22, 2021. \vspace{0.5em}
    %
    \entry*[2019] Invited Lecture, Yonsei University, Graduate School of Engineering, Computer Science Seminar
    \par \textbf{Blockchain Meets the Game Industry}, May 16, 2019. \vspace{0.5em}
    %
    \entry*[2018] Invited Talk, Korea Computer Graphics Society (KCGS) Conference
    \par \textbf{Mobile-Oriented AI-Based Augmented Reality: Practice and Case Studies}, Jul. 10, 2018.
    %
    \entry*[2017] Invited Lecture, Electronics and Telecommunications Research Institute (ETRI)
    \par \textbf{Applications and Practice of AI-Based Virtual Reality}, Dec. 4, 2017.
    %
    \entry*[2017] Invited Talk, KAIST ARRC
    \par \textbf{Applications and Practice of AI-Based Virtual Reality}, Nov. 23, 2017.
    %
    \entry*[2017] Invited Lecture, Kwangwoon University
    \par \textbf{Applications and Practice of AI-Based Virtual Reality}, Nov. 8, 2017.
\end{rubric}
